\Title

### 2023-02-10 Grimaldi-etal-BiolCybernetics.tex
Update on Overleaf.
2.1

To train and test our model, we need to define a dataset for which we control the direction and speed of motion. Let us now define a procedure for animating a natural scene with virtual eye movements, similar to those used in neurobiological~\citep{vinje_sparse_2000, baudot_animation_2013} and computational neuroscience~\citep{kremkow_push-pull_2016} studies. First, we draw a trajectory inspired by the biological movements of the eyes. Indeed, these movements allow us to dynamically actuate the center of vision, or gaze, in the visual field. In animals with a fovea, this is particularly useful because it allows the area with the highest density of photoreceptors in the environment to be moved, for example to a point of interest. A specific mechanism for this is called saccades, which are rapid eye movements that reposition the center of vision. In humans, saccades are very frequent (on average $2$ per second~\citep{dandekar_neural_2012}). They are generated very quickly (about $80~\ms$) and have a wide range of speeds. On a more microscopic scale, the human gaze moves with a continuous drift similar to a Brownian trajectory~\citep{poletti_head-eye_2015}. In order to maintain the full generality of the task, we will define eye movements using a form of random walk~\citep{engbert_integrated_2011}.This approach first defines a finite set of possible 2D movements in polar coordinates. Based on the distribution of biological movements, we simplified it by selecting a set of eye movements as the Cartesian product of $8$ linearly spaced movement directions and 3 geometrically spaced speeds. Next, we define a gaze trajectory as segments whose duration is drawn from a Poisson distribution with a mean block length of $20~\ms$, similar to a Lévy flight~\citep[p. 289]{mandelbrot_fractal_1982}. Finally, the trajectory is integrated, assuming first that the velocities are sampled uniformly and independently from the set of different motion sets, and second that the motion is uniform during a time segment. The resulting instances yield trajectories that are qualitatively similar to those observed for human eye movements (\seeFig{motion_task}-(left)).

@@

To transform each movie into events, we compute a gradient image (initialized at zero) by adding the gradient of the pixels' intensity over two successive frames. For a specific pixel and timestamp, an event is generated if the absolute value of this gradient exceeds a threshold. The event has either an OFF or ON polarity, respectively whether the gradient is negative or positive. This signed threshold value is then subtracted from the residual gradient image. When applied to the whole movie, the event stream is as a consequence similar to the output of a neuromorphic camera~\citep{rasetto_challenges_2022}, that is, a list of events defined by $x_\arank$ and $y_\arank$ (their position on the pixel grid), their polarity $\polev_\arank$ (ON or OFF) and time $\timev_\arank$  (\seeFig{motion_task}-(Right)). The goal here is to infer the correct motion solely by observing these events. 

@@

% \note{describe the heuristics inspired by neuroscience}

>>>>

To train and test our model, we need to define a dataset for which we control the direction and speed of motion. Let us now define a procedure for animating a natural scene with virtual eye movements, similar to those used in neurobiological~\citep{vinje_sparse_2000, baudot_animation_2013} and computational neuroscience~\citep{kremkow_push-pull_2016} studies. First, we draw a trajectory inspired by the biological movements of the eyes. Indeed, these movements allow us to dynamically actuate the center of vision, or gaze, in the visual field. In animals with a fovea, this is particularly useful because it allows the area with the highest density of photoreceptors in the environment to be moved, for example to a point of interest. A specific mechanism for this is called saccades, which are rapid eye movements that reposition the center of vision. In humans, saccades are very frequent (on average $2$ per second~\citep{dandekar_neural_2012}). They are generated very quickly (about $80~\ms$) and have a wide range of speeds. On a more microscopic scale, the human gaze moves with a continuous drift similar to a Brownian trajectory~\citep{poletti_head-eye_2015}. In order to maintain the full generality of the task, we will define eye movements using a form of random walk~\citep{engbert_integrated_2011}.This approach first defines a finite set of possible 2D movements in polar coordinates. Based on the distribution of biological movements, we simplified it by selecting a set of eye movements as the Cartesian product of $8$ linearly spaced movement directions \note{and 3 geometrically spaced speeds}. Next, we define a gaze trajectory as segments whose duration is drawn from a Poisson distribution with a mean block length of $20~\ms$, similar to a Lévy flight~\citep[p. 289]{mandelbrot_fractal_1982}. Finally, the trajectory is integrated, assuming first that the velocities are sampled uniformly and independently from the set of different motion sets, and second that the motion is uniform during a time segment. The resulting instances yield trajectories that are qualitatively similar to those observed for human eye movements (\seeFig{motion_task}-(left)).

@@

To transform each movie into events as the ones recorded by a DVS, we compute a gradient image (initialized at zero) by adding the gradient of the pixels' intensity over two successive frames. For a specific pixel and timestamp, an event is generated if the absolute value of this gradient exceeds a threshold. The event has either an OFF or ON polarity, respectively whether the gradient is negative or positive. This signed threshold value is then subtracted from the residual gradient image. When applied to the whole movie, the event stream is similar to the output of a neuromorphic camera~\citep{rasetto_challenges_2022}, that is, a list of events defined by $x_\arank$ and $y_\arank$ (their position on the pixel grid), their polarity $\polev_\arank$ (ON or OFF) and time $\timev_\arank$  (\seeFig{motion_task}-(Right)). The goal here is to infer the correct motion solely by observing these events. 

@@

\note{describe the heuristics inspired by neuroscience, remaining complex cells}
